\textbf{ Mapping stellar surfaces\\ I: Degeneracies in the rotational light curve problem }

### 2021-01-25 paper1/ms.tex

\begin{abstract}
    %
    Thanks to missions like \emph{Kepler} and \emph{TESS}, we now
    have access to tens of thousands of high precision, fast
    cadence, and long baseline stellar photometric observations.
    %
    In principle, these light curves encode a vast amount of information about
    stellar variability and, in particular, about the distribution of
    starspots and other features on their surfaces.
    %
    Unfortunately, the problem of inferring stellar surface properties
    from a rotational light curve is famously ill-posed;
    any inference that relies exclusively on the light curve
    of a single star is \emph{necessarily} prior-dominated.
    %
    The goal of this paper is twofold:
    (1) to explore the various degeneracies affecting the stellar
    light curve ``inversion'' problem and their effect on
    what can and cannot be learned from a stellar surface
    given unresolved photometric measurements; and
    (2) to motivate ensemble analyses of the light curves of
    many stars at once as a powerful method of breaking
    these degeneracies.
    %
    This is the first in a series of papers devoted to the development
    of novel algorithms and tools for the analysis of
    stellar light curves and spectral time series, with the
    explicit goal of enabling statistically robust inference
    about their surface properties.
\end{abstract}

>>>>

\begin{abstract}
    %
    Thanks to missions like \emph{Kepler} and \emph{TESS}, we now
    have access to tens of thousands of high precision, fast
    cadence, and long baseline stellar photometric observations.
    %
    In principle, these light curves encode a vast amount of information about
    stellar variability and, in particular, about the distribution of
    starspots and other features on their surfaces.
    %
    Unfortunately, the problem of inferring stellar surface properties
    from a rotational light curve is famously ill-posed;
    any inference that relies exclusively on the light curve
    of a single star is \emph{necessarily} prior-dominated.
    %
    The goal of this paper is twofold:
    (1) to explore the various degeneracies affecting the stellar
    light curve ``inversion'' problem and their effect on
    what can and cannot be learned from a stellar surface
    given unresolved photometric measurements; and
    (2) to motivate ensemble analyses of the light curves of
    many stars at once as a powerful method of breaking
    these degeneracies.
    %
    \dfm{While the examples in this paper focus on mapping stellar surfaces
        using photometric time series, the conclusions and proposed methods
        apply to more general problems, including applications where the stellar
        surface is a nuisance (exoplanet detection and characterization using
        transit light curves or radial velocities) or to spectral time series
        datasets (transmission spectroscopy and Doppler imaging).}
    %
    This is the first in a series of papers devoted to the development
    of novel algorithms and tools for the analysis of
    stellar light curves and spectral time series, with the
    explicit goal of enabling statistically robust inference
    about their surface properties.
\end{abstract}
